\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-29 paper.qmd
mapping oout remaining parts

keywords: [high-dimensional data, dimension reduction, triangulation, hexagonal binning, low-dimensional manifold, manifold learning, tour, data vizualization]
keywords-formatted: [high-dimensional data, dimension reduction, triangulation, hexagonal binning, low-dimensional manifold, manifold learning, tour, data vizualization]

@@

@@

- Summarise contributions
- Explain where it is expected or not expected to work, eg higher dimensional relationships
- Diagnostic app to explore differences in distances
- What might be useful enhancements

>>>>

keywords: [high-dimensional data, dimension reduction, hexagonal binning, low-dimensional manifold, tour, data vizualization, model in the data space]
keywords-formatted: [high-dimensional data, dimension reduction, hexagonal binning, low-dimensional manifold, tour, data vizualization, model in the data space]

@@

### What is the NLDR model?

### Notation

### Constructing the 2D model

### Displaying the model in $p-D$

### Measuring the fit

### What can be learned

@@

- Summarise contributions
- Explain where it is expected or not expected to work, eg higher dimensional relationships
- Human behaviour, the desire to have more certainty, and a tendency to prefer the well-separated views
- Diagnostic app to explore differences in distances
- What might be useful enhancements

### 2024-03-29 paper.tex
mapping oout remaining parts

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Looking at Non-Linear Dimension Reductions as Models in the Data Space},
  pdfauthor={Jayani P.G. Lakshika; Dianne Cook; Paul Harrison; Michael Lydeamore; Thiyanga S. Talagala},
  pdfkeywords={high-dimensional data, dimension
reduction, triangulation, hexagonal binning, low-dimensional
manifold, manifold learning, tour, data vizualization},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\noindent%
{\it Keywords:} high-dimensional data, dimension
reduction, triangulation, hexagonal binning, low-dimensional
manifold, manifold learning, tour, data vizualization
\vfill

@@

@@

\begin{itemize}
\tightlist
\item
  Summarise contributions
\item
  Explain where it is expected or not expected to work, eg higher
  dimensional relationships
\item
  Diagnostic app to explore differences in distances
\item
  What might be useful enhancements
\end{itemize}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Looking at Non-Linear Dimension Reductions as Models in the Data Space},
  pdfauthor={Jayani P.G. Lakshika; Dianne Cook; Paul Harrison; Michael Lydeamore; Thiyanga S. Talagala},
  pdfkeywords={high-dimensional data, dimension reduction, hexagonal
binning, low-dimensional manifold, tour, data vizualization, model in
the data space},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\noindent%
{\it Keywords:} high-dimensional data, dimension reduction, hexagonal
binning, low-dimensional manifold, tour, data vizualization, model in
the data space
\vfill

@@

\subsection{What is the NLDR model?}\label{what-is-the-nldr-model}

\subsection{Notation}\label{notation}

\subsection{Constructing the 2D model}\label{constructing-the-2d-model}

\subsection{\texorpdfstring{Displaying the model in
\(p-D\)}{Displaying the model in p-D}}\label{displaying-the-model-in-p-d}

\subsection{Measuring the fit}\label{measuring-the-fit}

\subsection{What can be learned}\label{what-can-be-learned}

@@

\begin{itemize}
\tightlist
\item
  Summarise contributions
\item
  Explain where it is expected or not expected to work, eg higher
  dimensional relationships
\item
  Human behaviour, the desire to have more certainty, and a tendency to
  prefer the well-separated views
\item
  Diagnostic app to explore differences in distances
\item
  What might be useful enhancements
\end{itemize}
